---
title: 'Exercise Sheet #6'
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Minh Son Tran (12424799)"
date: "2025-07-19"
output: distill::distill_article
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align  = "center"
)
```

## Exercise 1 : Building an R Package

### Functionality Requirements

I have successfully created the **rfetch** R package that meets all
specified requirements:

-   Working R package with proper functionality
-   Package is installable via GitHub
-   Contains 3 exported functions: `rfetch()`, `rfetch_info()`,
    `rfetch_theme()`
-   Documentation generated and up-to-date via `devtools::document()`
-   DESCRIPTION file properly formatted with dependencies and metadata

### Submission

#### a) Package Description

The **rfetch** package is a neofetch-style system information display
tool for R that shows user, host, OS, R version, and package information
with customizable color themes and ASCII logos. I chose this
functionality because it combines practical system information gathering
with visual appeal, making it useful for R users who want to showcase
their setup in a visually pleasing format similar to popular
command-line fetch tools.

#### b) GitHub Repository URL

<https://github.com/MinhSonTran97/rfetch>

#### c) Installation Command

```{r, eval=FALSE}
remotes::install_github("MinhSonTran97/rfetch")
```

**Installation tested and confirmed working.**
